Supplemental Materials: Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age 15 and Are Detected in Saliva

### 2021-11-11 Reports/Paper1.Rmd
added a chunk option to run data instead of loading

as_supp=T
stand_alone=T
```

```{r temp read n data}
basedir=here::here()
outdir=file.path(gsub('Code', 'Output', basedir), 'Figures')
datadir=gsub('Code', 'Data', basedir)
load(paste0(datadir, '/CreatedData/allPhenoData.Rdata'))
load(paste0(datadir, '/CreatedData/allmethyl.Rdata'))
load(paste0(datadir, '/CreatedData/completeCaseSVA.Rdata'))
load(paste0(datadir, '/CreatedData/methylation_summarymodels.Rdata'))
modeldata=modeldata %>% mutate(childteen=factor(childteen, levels=c('Age 9', 'Age 15')))%>%droplevels()%>%copy_labels(modeldata)
```

>>>>

as_supp=T
stand_alone=T
load_data=T
run_scripts=F
```

```{r temp read n data, eval=load_data}
basedir=here::here()
outdir=file.path(gsub('Code', 'Output', basedir), 'Figures')
datadir=gsub('Code', 'Data', basedir)
scriptdir=file.path(basedir, 'Scripts')
load(paste0(datadir, '/CreatedData/allPhenoData.Rdata'))
load(paste0(datadir, '/CreatedData/allmethyl.Rdata'))
load(paste0(datadir, '/CreatedData/completeCaseSVA.Rdata'))
load(paste0(datadir, '/CreatedData/methylation_summarymodels.Rdata'))
modeldata=modeldata %>% mutate(childteen=factor(childteen, levels=c('Age 9', 'Age 15')))%>%droplevels()%>%copy_labels(modeldata)
```

```{r sources scripts instead of loading, eval=run_scripts}
source(file.path(scriptdir, '01_clean_phenotype_data.R'))
source(file.path(scriptdir, '02_make_methyl_summary.R'))
#assuming 03_sva_variables.R has been run and exists separately as this would take a day to run. 
source(file.path(scriptdir, '04_summary_methyl_models.R'))
```
